Seurat processing for `r params$sample_id`

### 2024-11-25 analyses/cell-type-wilms-tumor-06/notebooks/01_seurat-processing.Rmd
move everything over to notebook, out of notebook_template

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message=FALSE,
                      warnings=FALSE)
```

@@

# select the 40 Wilms tumor single nucleus folders only
filedir <- filelist[grepl(params$sample_id, filelist)]

```

@@

  srat <- CreateSeuratObject(counts = counts(sce),
                             assay = "RNA",
                             project = sample_id
  )

@@

  # return Seurat object
  return(srat)

}

```

@@

```{r seurat_wf}
perform_norm_dimred_cluster <- function(srat,
                                        transform_method = "glmGamPoi",
                                        conserve_memory = TRUE,
                                        umap_dims = 1:50, 
                                        neighbors_dims = 1:50, 
                                        verbose = FALSE) {

  # Perform normalization, dimensionality reduction, and clustering on a 
  # Seurat object
  #
  # Arguments:
  #   srat: A Seurat object
  #   transform_method: The method passed to SCTransform(); glmGamPoi by default
  #   conserve_memory: Logical specifying whether or not SCTransform() should
  #                    conserve memory
  #   umap_dims: A vector of integers passed to RunUMAP() to specify the number 
  #              of dimensions; 1:50 by default
  #   neighbors_dims: A vector of integers passed to FindNeighbors() to specify
  #                   the dimensions of reduction to use as input
  #   verbose: Logical specifying whether or not functions should be verbose
  #
  # Returns: 
  #   A Seurat object containing all the contents of the normalization, PCA, 
  #   UMAP, neighbors, and clustering steps
  #

@@

  # Normalization
  options(future.globals.maxSize= 8912896000000)
  srat <- SCTransform(srat, 
                      method = transform_method,
                      verbose = verbose, 
                      conserve.memory = conserve_memory)

@@

  # Return
  return(srat)

}

```

@@

```{r run_seurat_wf, fig.height=4, fig.width=8, warning=FALSE, out.width='100%'}

srat <- convert_sce_to_seurat(sce, 
                                  sample_id = params$sample_id)

srat <- perform_norm_dimred_cluster(srat,
                                        transform_method = "glmGamPoi",
                                        conserve_memory = TRUE,
                                        umap_dims = 1:50, 
                                        neighbors_dims = 1:50, 
                                        verbose = FALSE)
```

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("01-Seurat_", params$sample_id,".Rds")))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warnings = FALSE
)
```

@@

# select the 40 Wilms tumor single nucleus folders only
filedir <- filelist[grepl(params$sample_id, filelist)]
```

@@

  srat <- CreateSeuratObject(
    counts = counts(sce),
    assay = "RNA",
    project = sample_id
  )

@@

  # return Seurat object
  return(srat)
}
```

@@

```{r seurat_wf}
perform_norm_dimred_cluster <- function(srat,
                                        transform_method = "glmGamPoi",
                                        conserve_memory = TRUE,
                                        umap_dims = 1:50,
                                        neighbors_dims = 1:50,
                                        verbose = FALSE) {
  # Perform normalization, dimensionality reduction, and clustering on a
  # Seurat object
  #
  # Arguments:
  #   srat: A Seurat object
  #   transform_method: The method passed to SCTransform(); glmGamPoi by default
  #   conserve_memory: Logical specifying whether or not SCTransform() should
  #                    conserve memory
  #   umap_dims: A vector of integers passed to RunUMAP() to specify the number
  #              of dimensions; 1:50 by default
  #   neighbors_dims: A vector of integers passed to FindNeighbors() to specify
  #                   the dimensions of reduction to use as input
  #   verbose: Logical specifying whether or not functions should be verbose
  #
  # Returns:
  #   A Seurat object containing all the contents of the normalization, PCA,
  #   UMAP, neighbors, and clustering steps
  #

@@

  # Normalization
  options(future.globals.maxSize = 8912896000000)
  srat <- SCTransform(srat,
    method = transform_method,
    verbose = verbose,
    conserve.memory = conserve_memory
  )

@@

  # Return
  return(srat)
}
```

@@

```{r run_seurat_wf, fig.height=4, fig.width=8, warning=FALSE, out.width='100%'}
srat <- convert_sce_to_seurat(sce,
  sample_id = params$sample_id
)

srat <- perform_norm_dimred_cluster(srat,
  transform_method = "glmGamPoi",
  conserve_memory = TRUE,
  umap_dims = 1:50,
  neighbors_dims = 1:50,
  verbose = FALSE
)
```

@@

```{r save}
saveRDS(object = srat, file = file.path(output_dir, paste0("01-Seurat_", params$sample_id, ".Rds")))
```
